Hybrid MILP to efficiently and accuratly \\ solve hard DNN verification instances

### 2024-09-18 ICLR25/formula.tex
update formula.tex

Then $-D(a)$ is the estimation of improvement of upper bound of $a$ by opening node $b$. For the lower bound, we can compute $D(a)$ by the same formula with the $v$ for lower bound LP solution and negative weights instead. This is the formula to compute improvement of nodes two layers before.

@@

This formula is based on previous subsection but more complex. In some network, running this formula may cost too much time but obtain little accuracy.

@@

\begin{definition}\label{3layer}
	For a fixed target node $a$ and a fixed source node $b$ in three layers before $a$. Let $\UB$ and $\LB$ denote the precomputed upper bounds and lower bound used in building MILP models. To compute the improvement of of upper bound of $a$ by $b$, let $v$ be the function of solutions of LP model; then we define the following function $h$ for all nodes $c$ in 2 layers before the target node $a$ as follows:
	\begin{align}
		&v_0 = v(\hat{c}), v_1 = \ReLU(v(c)), v_2 = \frac{\UB(c)v(c)-\UB(c)\LB(c)}{\UB(c)-\LB(c)}\\
		&h(c) =
		\begin{cases}
			\frac{v_0-v_1}{v_2-v_1}, & \text{if } v_2-v_1 > 0\\
			0.5, & \text{otherwise.}
		\end{cases}
	\end{align} 
\end{definition}

@@

	To compute $D(d)$ for nodes $d$ in one layer before $a$, we define 
	\begin{align}
		&w_0 = \sum_c D(c)W_{cd}\\
		&w_1 = \min(\UB(d),v(d)+w_0)\\		
		&D(d) =
		\begin{cases}
			w_1-v({d}), & \text{if }W_{da} > 0 \text{ and } \LB(d)\geq 0\\
		k(d)(w_1-v({d})), & \text{if }W_{da} > 0 \text{ and } \LB(d)< 0\\
		\ReLU(w_1)-v(\hat{d})	, & \text{if }  W_{da} < 0
		\end{cases}\\
		&D(a) = \sum_d D(d)W_{da}
	\end{align}
\end{definition} $-D(a)$ is the estimation of improvement of upper bound of $a$ by opening node $b$.  For the lower bound, we can compute $D(a)$ by the same formula with the $v$ for lower bound LP solution and negative weights  instead.

>>>>

Then $-D(a)$ is the estimation of improvement of upper bound of $a$ by opening node $b$. For the lower bound, we can compute $D(a)$ by the same formula with the function $v$ from lower bound LP solution and negative $-W_{ca}$ instead. This is the formula to compute improvement of nodes two layers before.

@@

This formula is based on previous subsection but more complex. In some network, running this formula may cost too much time.

@@

\begin{definition}\label{3layer}
	Suppose we have a fixed target node $a$ and a fixed source node $b$ in three layers before $a$. Let $\UB$ and $\LB$ denote the precomputed upper bounds and lower bound used in building MILP models. To compute the improvement of of upper bound of $a$ by $b$, let $v$ be the function of solutions of LP model; then we define the following function $h$ for all nodes $c$ in 2 layers before the target node $a$ as follows:
	\begin{align}
		&v_0 = v(\hat{c}), v_1 = \ReLU(v(c)), v_2 = \frac{\UB(c)v(c)-\UB(c)\LB(c)}{\UB(c)-\LB(c)}\\
		&h(c) =
		\begin{cases}
			\frac{v_0-v_1}{v_2-v_1}, & \text{if } v_2-v_1 > 0\\
			0.5, & \text{otherwise.}
		\end{cases}
	\end{align} 
\end{definition}

@@

	To compute $D(d)$ for nodes $d$ in one layer before $a$, we define 
	\begin{align}
		&w_0 = \sum_c D(c)W_{cd}\\
		&w_1 = \min(\UB(d),v(d)+w_0)\\		
		&D(d) =
		\begin{cases}
			w_1-v({d}), & \text{if }W_{da} > 0 \text{ and } \LB(d)\geq 0\\
		k(d)(w_1-v({d})), & \text{if }W_{da} > 0 \text{ and } \LB(d)< 0\\
		\ReLU(w_1)-v(\hat{d})	, & \text{if }  W_{da} < 0
		\end{cases}\\
		&D(a) = \sum_d D(d)W_{da}
	\end{align}
\end{definition} $-D(a)$ is the estimation of improvement of upper bound of $a$ by opening node $b$.  For the lower bound, we can compute $D(a)$ by the same formula with the function $v$ from lower bound LP solution and negative $-W_{da}$  instead.
